\documentclass[12pt,a4paper]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Input header file 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../../../TexScripts/HeaderfileTexDocs}

%%%%%%%%%%%%%%%%%%% To change the margins and stuff %%%%%%%%%%%%%%%%%%%
\geometry{left=0.8in, right=0.9in, top=0.9in, bottom=0.8in}
%\setlength{\voffset}{0.5in}
%\setlength{\hoffset}{-0.4in}
%\setlength{\textwidth}{7.6in}
%\setlength{\textheight}{10in}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Comments on consulting session with live client}
\author{Subhrangshu Nandi\\
  Stat 998; Spring 2016}
\date{February 23, 2016}
%\date{}

\maketitle

\begin{enumerate}
\item [(1)] Identify 2 actions (in terms of the topics mentioned on the handout) that you think the consultant performed well. (Cite the specific examples!!) Explain (very briefly) what was good about each.
\begin{enumerate}
\item[(a)] The consultant did an excellent use of ``play-back'' technique at various stages of the conversation to ensure that he exactly understood what the client was trying to express. Some examples are when he asked precisely about the orientation of the petri-dish, and when he ensured how the observations are recorded and measured.

\item[(b)] Throughout the conversation the consultant maintained interest in the client's scientific problem and his goals. He realized that the client did not have a crystal clear idea of what the statistical question is. That's when he tried to engage the client in discussions that could lead to designing a pilot experiment which could subsequently help with asking the right scientific question. The client was very pleased with the consultant's demeanor and his interest in the problem.
\end{enumerate}

\item [(2)] Identify 2 actions (in terms of the topics mentioned on the handout) that you think the consultant performed badly. (Cite the specific examples!!) Explain (very briefly) what was bad about each.
\begin{enumerate}
\item[(a)] In the end it was not clear if the client had a clear idea of what the immediate next steps would be. The consultant could have perhaps summarized the discussion by making sure both he and the client were aware of what each other's expectations were. 

\item[(b)] It was not clear if the consultant could gauge the client's statistical background, nor the extent to which he wanted a statistician's involvement in the problem.
\end{enumerate}

\item [(3)] Briefly describe your perceptions on what the scientist/client was feeling during the session. \\
The client and the consultant were both very engaged in the discussion. The client was happy about the consultant's continued interest in his scientific question. He was very receptive to the consultant's questions and answered them to the best of his abilities. He seemed very knowledgable about his research problem and expressed eagerness to explore this particular topic. Both of them were very cordial and polite throughout the conversation. Even when it became evident that there isn't a clea research goal, there was no unpleasantness in the conversation. Overall, it was a great learning experience watching the consultant-client interaction.
\end{enumerate}


\end{document}


